Rough Draft

### 2017-11-13 Article submission/roughdraft.tex
edited results

    However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated. A majority of existing research focuses on assessing and predicting question and answer quality. Therefore, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``failure'' probability of a question.

@@

    Questions analyzed were restricted to those posted in English (97\% of the full data). The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times (questions can still receive answers after the download date).

@@

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to include in the full Cox proportional hazards model. Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.

@@

  Of 7,760 questions, 63.8\% received an answer by the download date. Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer. The following statistics were calculated from Kaplan-Meier estimates of survival probability. The mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours. Table 1 provides more percentiles of survival time. Figure B shows the Kaplan-Meier curve for all questions in the data. The curve indicates that at around 100 hours after a question is posted, survival probability remains constant at around 0.35.

Predictors with p-values less than 0.01 in univariate analysis are in table b, and were included in the full Cox model for cross-validation. Average metrics for test and training sets are in table c. Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit. Restricted cubic splines were fit to continous predictors. Splines of five knots were fit to the average frequency of question's tags as well as to the number of characters in the user-defined device name. Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text. Results of cross-validation for the model including the splines are in table d. As refitting the model without insignificant predictors did not effect predictive performance, all variables were included. The final model, with all variables described above including splines, was fit to the full data.

>>>>

    However, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated. As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.

@@

    Questions analyzed were restricted to those posted in English (97\% of the full data). The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.

@@

  Of 7,760 questions, 63.8\% received an answer by the download date. Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer. Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours. Table 1 provides additional percentiles of survival time.

Predictors with p-values less than 0.01 in univariate analysis, shown in table b, were included in the full Cox model for cross-validation. Average metrics for test and training sets are in table c. Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit. Examining model parameters of the training models showed that the the average frequency of a question's tags had an extremely high coefficient (> 20). To address this, a square root transformation was applied. Restricted cubic splines were fit to continous predictors. A spline of five knots was fit to the number of characters in the user-defined device name. Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text. Results of cross-validation for the model including the splines are in table d. As refitting the model without insignificant predictors did not effect predictive performance, all variables were included. The final model, with all variables described above including splines, was fit to the full data.
